%\addcontentsline{toc}{section}{参考文献}

\begin{thebibliography}{unstr} 
  \bibliographystyle{gbt7714}
  \addtolength{\itemsep}{-1ex}  % 缩小行距

  \bibitem{RefA}
  % Format for Journal Reference
  Author, Article title, Journal, Volume, page numbers (year)
  % Format for books
  \bibitem{RefB}
  Author, Book title, page numbers. Publisher, place (year)
  % etc
    \bibitem{1993}C. S. Lent, P. D. Tougaw, W. Porod, and G. H. Bernstein, ``Quantum cellular automata," Nanotechnology, Vol. 4, No. 1, pp. 49, 1993.
    \bibitem{2017NNI}A. Bharti and A. Sharma, ``Implementation of exor gate using qca with nni logic," IEEE WiSPNET, pp. 2027-2031, 2017.
    \bibitem{1961}R. Landauer, "Irreversibility and heat generation in the computing process," IBM journal of research and development, Vol. 5, No. 3, pp. 183-191, 1961.
    \bibitem{NNI-eq} K. Das and D. De, ``Characterization, test and logic synthesis	of novel conservative and reversible logic gates for qca," International Journal of Nanoscience, Vol. 9, No. 3, pp. 201-214, 2010.
    \bibitem{2019base}J. C. Das and D. De, ``Novel design of reversible priority encoder in quantum dot cellular automata based on toffoli gate and feynman gate," The Journal of Supercomputing, Vol. 75, No. 10, pp. 6882-6903, 2019.
    \bibitem{QCAdesigner}K. Walus, T. J. Dysart, G. A. Jullien, and R. A. Budiman, ``Qcadesigner: a rapid design and simulation tool for quantum-dot cellular automata," IEEE Trans. Nanotechnol., Vol. 3, No. 1, pp. 26-31, 2004.
    
    

\end{thebibliography}

\bibliographystyle{gbt7714}
\bibliography{ref}

  %  \begin{thebibliography}
  %  @article{SVM003,
  %title={Applications of support vector machine (SVM) learning in cancer genomics},
  %author={Huang, Shujun and Cai, Nianguang and Pacheco, Pedro Penzuti and Narrandes, Shavira and Wang, Yang and Xu, Wayne},
  %journal={Cancer genomics \& proteomics},
  %volume={15},
  %number={1},
  %pages={41--51},
  %year={2018},
  %publisher={International Institute of Anticancer Research}
  %  }

  %  @article{ref10,
  %title={个性化推荐算法设计},
  %author={赵亮 {,}~ 胡乃静{,}~ 张守志},
  %journal={计算机研究与发展},
  %volume={39},
  %number={8},
  %pages={986--991},
  %year={2002}
  %  }
 
%\end{thebibliography}
  